### 2020-01-18 all_models.tex
updated Table 3

\charles{Still preliminary, only 309 data points here}
\paragraph{Results}
\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|}
\hline
    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
$R^{2}$ (mean)  & 0.61 & 0.59 & 0.66 & 0.66 \\
$R^{2}$ (std)   & 0.35 & 0.37 & 0.30 & 0.30 \\
\hline
$MSE$ (mean)    & 3.60 &  7.19 & 2.44 & 2.28 \\
$MSE$ (std)     & 7.64 & 20.13 & 4.57 & 4.43 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across XX datasets, covering 228 different pretrained DNNs.  We only cinclude regressions for architecturs with 5 or more data points \charles{and which are postively correlated with the test error}.}
\label{table:nlp}
\end{table}

>>>>

\charles{Still preliminary, only 309 data points here}
\paragraph{Results}
\begin{table}[t]
\small
\begin{center}
\begin{tabular}{|p{1in}|c|c|c|c|}
\hline
    & Frobenius Norm & Spectral Norm & Weighted Alpha & Alpha-Norm \\
    & $\langle\log\Vert\mathbf{W}\Vert_{F}\rangle$ & $\langle\log\Vert\mathbf{W}\Vert_{\infty}\rangle$ & $\langle\hat{\alpha}=\alpha\log\lambda_{max}\rangle$ & $\langle\log\Vert\mathbf{X}\Vert^{\alpha}_{\alpha}\rangle$ \\
\hline
$R^{2}$ (mean) & 0.63 &0.55 &0.64 &0.64 \\
$R^{2}$ (std)  & 0.34 &0.36 &0.29 &0.30 \\
\hline
$MSE$ (mean)   & 4.54 &9.62 &3.14 &2.92 \\
$MSE$ (std)    & 8.69 &23.06 &5.14 &5.00 \\
\hline
\end{tabular}
\end{center}
\caption{Comparison of linear regression fits for different average log norm metrics across XX datasets, covering 168 (out of 309) different pretrained DNNs.  We only cinclude regressions for architecturs with 4 or more data points \charles{and which are postively correlated with the test error?}.  These results can be readily reproduced using the Google Colab notebooks accompanying thie paper\cite{notebooks}}
\label{table:nlp}
\end{table}
